### 2018-11-09 Sabanci_talk/Sabanci_talk.tex
2 more slides, several more figures

\begin{frame}{Case study: GW170817}

@@

@@

\begin{frame}{Supplement 1: mode suppression}
\begin{itemize}
 \item For $q=1$ due to symmetry only (2,2), (3,2), (4,2), (4,4) are nonzero 
 \item For $q\ne 1$ all $\ell \ge 2$ modes exist, but are much smaller than $(2,2)$
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Case study: GW170817}
\begin{itemize}
  \item 17 August 2017, signal swept from $f\approx 30\,$Hz to $2000\,$Hz 
  \item The event lasted $\approx 57\,$seconds, $\approx 3000$ GW cycles, $\rho_\text{tot} = 32.4$
  \item Followed by GRB170817A 1.7 seconds later
  \item Rapid localization using L1-H1-V1 $\sim 30\,\text{deg}^2$
  \item Optical counterpart in NGC 4993 11 hours later
\end{itemize}

  \begin{columns}
  \begin{column}{0.5\textwidth}  %%<--- here
      \begin{center}
      \includegraphics[height=4cm]{figs/GW_GRB170817.jpg}
      \end{center}
  \end{column}
  \begin{column}{0.5\textwidth}
  %
    Assuming low spin priors\\
    $ M=2.73^{+0.04}_{-0.01} M_\odot$ \\
    $ M_c =1.186^{+0.001}_{-0.001}M_\odot $ \\ 
    $ D=40.7^{+2.36}_{-2.36}\text{Mpc} $ \\
    \red{Note:} $M_c$ has the best precision: 
  \begin{small}${\dot{f}} = \f{96}{5}\pi^{8/3} \left(\tfrac{G M_c}{c^3}\right)^{5/3}\, {f^{11/3}}$ \end{small}

    \end{column}
  \end{columns}

@@

\begin{frame}{Case study: GW170817}  {Let's put our knowledge to the \red{test}}
\vspace{-7mm}
  \begin{footnotesize}
    \begin{align*}
      &\tau_\text{insp}^{0\text{PN}} \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2680 \hspace{2cm} (M=2.74 M_\odot) \\
      &\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \hspace{2cm} (f_\text{ISCO}\simeq 1605\,\text{Hz}) 
    \end{align*}
  \end{footnotesize}
  What about the SNR? \quad
  \begin{small}$\rho_{\text{tot},\llcorner}  = {\bar\rho_c(f_0)\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}$   
  \end{small}
  %

%
\begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2cm,-2.cm)}]current page.center) {\includegraphics[height=5cm]{../Figures/GW170817_strains.pdf}};
    \onslide<1->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-0.3cm)}]current page.center) 
    {\begin{footnotesize} 
      $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
    \end{footnotesize}}; 
    \onslide<1->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-1.3cm)}]current page.center) 
    {\begin{footnotesize} 
      $ \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}$    
    \end{footnotesize}};  
    \onslide<1->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.3cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_h = 29.2,\quad \bar\rho_m = 14.6,\quad \bar\rho_l = 6.11 $    
    \end{footnotesize}}; 
    \onslide<1->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.6cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_\text{L1} = 26.4 \quad 18.8 \quad 2.0 $    
    \end{footnotesize}};
    \onslide<1->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.6cm)}]current page.center) 
    {\begin{footnotesize} 
      $\rho_\text{tot} = 32.6 $    
    \end{footnotesize}};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Supplement 1: mode suppression}
\begin{itemize}
 \item For $q=1$ due to symmetry only (2,2), (3,2), (4,2), (4,4) are nonzero 
 \item For $q\ne 1$ all $\ell \ge 2$ modes exist, but are much smaller than $(2,2)$
\end{itemize}
\begin{align*}
      x &=1
	  %
	  %\\
	  %
      \end{align*}
\end{frame}
